Capstone Movielens Report

### 2025-10-26 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function: msg.set_arg.

This function is a wrapper to [logr::log_open](https://www.rdocumentation.org/packages/logr/versions/1.3.9/topics/log_open) function. It also calls internally the following functions to generate a unique file name based on the [file_name](#func.open_logfile.args.file_name) argument and _system time_:

@@

This function internally calls [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format value specified by the [arg](#func.msg.set_arg.args.arg)  argument to replace all occurances of the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument (`%1` by default).

@@

>>>>

This function is a wrapper for the [logr::log_open](https://www.rdocumentation.org/packages/logr/versions/1.3.9/topics/log_open) function. It also calls internally the following functions to generate a unique file name based on the [file_name](#func.open_logfile.args.file_name) argument and _system time_:

@@

This function is a wrapper for the [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` function, which is called internally to replace all occurrences of the substring specified by the [arg_name](#func.msg.set_arg.args.arg.name) argument, in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument (`%1` by default).

@@

The character vector returned by the internally called [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
